---
title: "reverse_engineering_part_2"
format: html
editor: visual
---

## Nearly **250 women have been fatally shot by police since 2015**

**As with fatal police shootings of men, the vast majority of the women killed were armed with a potential weapon at the time, although slightly less often: 89 percent of the women were armed, compared to 91 percent of the men.**

```{r}
library(janitor)
library(tidyverse)
```

Our first step was the find the data from The Washington Post and

```{r}

#download the data
police_shooting <- read_csv("~/Documents/Github/fatal-police-shootings-data (2).csv")
View(fatal_police_shootings_data_2_)

```

Add description about what I'm doing here

```{r}

women_police_shooting <- police_shooting %>% 
  filter(gender == "F", date < "2020-09-04") %>% 
  select (gender, armed, date)
  view(women_police_shooting)
  

men_police_shooting <- police_shooting %>% 
  filter(gender == "M", date < "2020-09-04") %>% 
  select (gender, armed, date)
  view(men_police_shooting)

```

**Since The Washington Post began [tracking fatal shootings by police](https://www.washingtonpost.com/graphics/investigations/police-shootings-database/) in 2015, officers have fatally shot 247 women out of the more than 5,600 people killed overall. Of the 247 women fatally shot, 48 were Black and seven of those were unarmed.**

```{r}

  

```

\
